---
title: Downloads In Africa
author: John Waller
date: '2018-06-06'
slug: downloads-in-africa
categories:
  - GBIF
  - R
  - Africa
tags:
  - GBIF
  - Africa
  - R
---


## Total Occurrence Downloads In Africa

Here we see that **South Africa** dominates the number of occurrence downloads coming from Africa with around **12k** total downloads, since GBIF started recording download data in 2013. 

Other countries have very few downloads when compared to **South Africa**, with some countires having as **few as 1-3 downloads since 2013**. 

```{r, echo=FALSE, warning=FALSE,message=FALSE, fig.height=7,fig.width=10}
library(highcharter)
require(dplyr) 

load("C:/Users/ftw712/Desktop/africaStats/data/africaDownloads.rda")

hcmap("https://code.highcharts.com/mapdata/custom/africa.js",data=africaDownloads,joinBy="name",value="downloads",name = "total downloads",
tooltip = list(valueSuffix = " downloads"))

```

## Occurrence Downloads In Africa Through Time

Here we see the number of downloads in Africa through time. **South Africa** here again has the most downloads on average. 

If you click on the United States, you can see how **africa total downloads** compares to the country with the most downloads, the **United States**. Other African countries with a relatively large amount of downloads are also plotted. 

```{r, echo=FALSE, warning=FALSE,message=FALSE, fig.height=7,fig.width=10}
source("C:/Users/ftw712/Desktop/africaStats/R/africaDownloadsThroughTime.r")
africaDownloadThroughTime()

```


## How Does Africa Compare To Other Countries And Continents? 

All countries with over **1000 total downloads** are shown. I have also included **total africa**, which is all of the downloads coming from the continent as a whole. 
**Africa** is definitely not requesting as many downloads as **Europe** or the **Americas**, but is producing more downloads than **India**, and both regions have approximately the same population. 

```{r, echo=FALSE, warning=FALSE,message=FALSE, fig.height=7,fig.width=10}
source("C:/Users/ftw712/Desktop/africaStats/R/africaDownloadBarChart.r")

africaDownloadBarChart()
```




